Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-27 fmics/paper.tex
add statements of 6 theorems
and names of 6 more that would probably be needed if I want to go
through any proofs...

\begin{figure}
\caption{
Definitions of auxiliary HOL functions used while proving theorems about the model of the SRS structure.
\label{fig:auxdefs}
}
\begin{align*}
\mathsf{delay\_sum}\;0&=0\\
\mathsf{delay\_sum}\;n&=\mathsf{delay}\;n'+\mathsf{delay\_sum}\;n'\\
&\qquad\text{where $(n',\_)=\mathsf{input}\;n$}
\end{align*}
\begin{align*}
\mathsf{last\_update}\;n\;0&=0\\
\mathsf{last\_update}\;n\;t&=\text{if $\mathsf{update\_time}\;n\;t$ then $t$}\\
&\qquad\text{else }\mathsf{last\_update}\;n\;(t-1)\qquad\text{(where $t>0$)}
\end{align*}
\end{figure}

\begin{multline*}
\forall{D\,n\,x\,t}.\,{0 < n}\land{\mathsf{update\_time\;n\;t}}\implies\\\mathsf{output}\;D\;n\;x\;t=\sum_{m=0}^{((\mathsf{tap}\;n\;x)+1)\times(\mathsf{delay}\;n)-1}\begin{cases}0&t<m+\mathsf{delay\_sum}\;n\\D\;(t-m-\mathsf{delay\_sum}\;n)&\text{otherwise}\end{cases}
\end{multline*}

%One of our objectives in formally modelling SRS was to keep the topology parameterized.
%It is likely that the configuration of the slices and shift registers will in the future change to accommodate higher precision.
%A parameterized model can be used both for current and future versions of the system.
%For this, we formalized the definitions of the model by six parameters:

>>>>

\begin{figure}
\caption{
Definitions of auxiliary HOL functions used while proving theorems about the model of the SRS structure.
\label{fig:auxdefs}
}
\begin{align*}
\mathsf{delay\_sum}\;0&=0\\
\mathsf{delay\_sum}\;n&=\mathsf{delay}\;n'+\mathsf{delay\_sum}\;n'\\
&\qquad\text{where $(n',\_)=\mathsf{input}\;n$}
\end{align*}
\begin{align*}
\mathsf{last\_update}\;n\;0&=0\\
\mathsf{last\_update}\;n\;t&=\text{if $\mathsf{update\_time}\;n\;t$ then $t$}\\
&\qquad\text{else }\mathsf{last\_update}\;n\;(t-1)\qquad\text{(where $t>0$)}
\end{align*}
\begin{align*}
\mathsf{exact}\;D\;n\;x\;t=\sum_{m=0}^{((\mathsf{tap}\;n\;x)+1)\times(\mathsf{delay}\;n)}\begin{cases}0&t<m+1\\D\;(t-m-1)&\text{otherwise}\end{cases}
\end{align*}
\end{figure}

\begin{figure}
\caption{
A selection of theorems about our model proved using HOL4.
\label{fig:theorems}
}
\begin{equation}\label{update_time_last_update}
\forall{n\,t}.\,\mathsf{update\_time}\;n\;(\mathsf{last\_update}\;n\;t)
\end{equation}
\begin{equation}\label{last_update_thm}
\forall{n\,t}.\,\mathsf{last\_update}\;n\;t=t-t\operatorname{mod}\mathsf{delay}\;n
\end{equation}
%SR_prev
%SR_first
\begin{equation}\label{output_last_update}
\forall{D\,n\,x\,t}.\,\mathsf{output}\;D\;n\;x\;t=\mathsf{output}\;D\;n\;x\;(\mathsf{last\_update}\;n\;t)
\end{equation}
\begin{equation}\label{output_sum}
\forall{D\,n\,x\,t}.\,{0<n}\implies\mathsf{output}\;D\;n\;x\;t=\sum_{m=0}^{\mathsf{tap}\;n\;x}\mathsf{SR}\;D\;n\;m\;t
\end{equation}
%output_first
%output_source_at_update_times
%output_prev_at_update_times
\begin{multline}\label{output_input_at_update_times}
\forall{D\,n\,x\,t}.\,{0 < n}\land{\mathsf{update\_time\;n\;t}}\implies\\\mathsf{output}\;D\;n\;x\;t=\sum_{m=0}^{((\mathsf{tap}\;n\;x)+1)\times(\mathsf{delay}\;n)-1}\begin{cases}0&t<m+\mathsf{delay\_sum}\;n\\D\;(t-m-\mathsf{delay\_sum}\;n)&\text{otherwise}\end{cases}
\end{multline}
\begin{multline}\label{output_eq_exact}
\forall{D\,n\,x\,t}.\,{0 < n}\implies\\\mathsf{output}\;D\;n\;x\;t=\begin{cases}0&\mathsf{last\_update}\;n\;t<\mathsf{delay}\;n\\\mathsf{exact}\;D\;n\;x\;(\mathsf{last\_update}\;n\;t+1-\mathsf{delay\_sum}\;n)\end{cases}
\end{multline}
%max_error
\end{figure}
